Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2024-01-02 demystify.tex
updates

\paragraph{Self-written Letters} Many international students write letters themselves (typically due to the requests of their profs.) and have them signed by their profs. Such letters have little values and would be considered weak by reviewers, who can question why you cannot even find someone cares enough about you to write a candid personal reference letter.  Instead of the reference writer writing about you, in this case it is you who write about yourself (and they just sign the letter).

@@

\begin{commentbox}[Vu:]
  Some letter writers ask the applicants to write their own letters for them to sign. As mentioned, this will hurt the applicants (admission committee members are actually quite good at determining this)! Multiple students mentioned that  some professor did this so that the applicants do not go abroad or only go to places where they want the students to go to.
  \tcblower
  Sometimes students would go through great length just to get letters from well-known professors in their school, but the letters are generic and carry little value, in fact, \red{red flags}. Moreover, a top professor in Vietnam might not be well-known to US faculty (see more details in \S\ref{sec:your-school}). So save the trouble and just get letters from \emph{any} professors/supervisors who knows you well and can write a good letter about your research ability. It's better to have a good personalized
  letter about your own research ability from someone who is less
  well-known than a generic/weak letter from a well-known person.
\end{commentbox}

@@

>>>>

\paragraph{Self-written Letters} Many international students write letters themselves, typically due to the requests of their profs., and have them signed by their profs. Such letters have little values and are considered weak by reviewers (why can you not even find someone who cares or knows enough about you to write a candid personal reference letter?).  Instead of the reference writer talking about you, in this case it is you who write about yourself (and they just sign the letter).

@@

@@

\begin{commentbox}[Vu:]

    Another sad reality is that some professors are unwilling to write letters or write weak ones because they do not want (good) students to go abroad or only go to places where they want the students to go to. If you are in this situation, you should find someone else to write for you.
    \tcblower

    Sometimes students would go through great length just to get letters from well-known professors in their school (e.g., department head). But as mentioned, if these professors do not know you, the letters are generic and carry little value, in fact, \red{red flags}. Moreover, a top professor in Vietnam might not be well-known to US faculty (see more details in \S\ref{sec:your-school}). So save the trouble and just get letters from \emph{any} professors/supervisors who knows you well and can write a good letter about \emph{your} research ability. It's better to have a good personalized
    letter about your own research ability from someone who is less
    well-known than a generic/weak letter from a well-known person.

  \end{commentbox}
